\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

\begin{minipage}[t]{0.40\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Mateusz}}}}} % First name

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Tracz}}}}} % Last name

	\vspace{6pt}

\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Warsaw}\\
	\icon{Phone}{12}{+48 605 063 069}\\
	\icon{At}{12}{\href{mailto:matishadow@gmail.com}{matishadow@gmail.com}}\\
\end{minipage}
\begin{minipage}[t]{0.280\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Edit}{12}{\href{https://matishadow.github.io/matishadowblog/posts}{Blog}}\\
	\icon{Github}{12}{\href{https://github.com/matishadow}{GitHub Profile}}\\
	\icon{Globe}{12}{\href{https://about.me/matishadow}{about.me/matishadow}}\\
\end{minipage}

\cvsect{Who Am I?}

\begin{minipage}[t]{0.46\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	Senior Software Engineer with 8+ years of experience in full-stack development, specializing in .NET, Azure, and React. 
	Passionate about building high-quality clean solutions and reverse-engineering systems to gain a deep understanding of their inner workings. 
	Proven track record of designing complex features and mentoring team members.

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{.NET}{100}
		\baritem{React/JS}{70}
		\baritem{HTML/CSS}{70}
		\baritem{SQL}{60}
		\baritem{Python}{50}
		\baritem{C/x86}{50}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{1/Azure, 2/{Rider/Vim}, 2/{EF Core},  1/Networks, 2/TDD,  2/Git, 1/Security, 1/Linux, 1/AsciiDoc}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{07.2021--now}
		{Senior Software Developer}
		{Netcompany}
		{
		  Building multi-platform solution for media representatives, using \textbf{Azure Functions} and \textbf{React}.
		  \begin{itemize}
		  	\setlength\itemsep{0pt}
			\itemindent=-13pt
			\item Designing and implementing complex features like \textbf{highly customizable form} or \textbf{live RSS feed}.
			\item Improving quality by introducing \textbf{Clean Architecture}, \textbf{unit testing} and \textbf{functional paradigms}.
			\item Optimizing performance and stability by using \textbf{Redis} for caching and \textbf{Polly} for integrations.
			\item Performing code reviews, cross-team collaboration, \textbf{mentoring} juniors and technical interviews.
		  \end{itemize}
		}
	\entry
		{08.2020--12.2020}
		{Software Developer}
		{Netcompany}
		{
		  Developing \textbf{ASP.NET Web API} for COVID-19 contact tracing app, used in Denmark and Norway.
		  \begin{itemize}
		  	\setlength\itemsep{0pt}
			\itemindent=-13pt
			\item Using \textbf{OpenSSL} for integration with EU Federation Gateway Service.
		  \end{itemize}
		}
	\entry
		{09.2017--07.2020}
		{Software Developer}
		{Consafe Logistics}
		{
		  Developing and maintaining warehouse management system.
		  \begin{itemize}
		  	\setlength\itemsep{0pt}
			\itemindent=-13pt
			\item Working with legacy codebase consisting of \textbf{C/Cpp} server and \textbf{WinForms} .NET clients.
			\item Writing \textbf{Python} scripts for Git flow, CI/CD, and scheduled maintenance jobs.
			\item Conducting technical interviews for recruitment process. 
		  \end{itemize}
		}
	\entry
		{02.2017--07.2017\\\footnotesize{part time}}
		{Junior .NET Developer}
		{Nexio Management}
		{
		  Maintaining case management portal, written in \textbf{ASP.NET MVC}.
		}
	\entry
		{06.2016--09.2016}
		{.NET Internship}
		{Billennium}
		{
		  Implementing platform for managing and distributing Azure DevOps notifications to Skype.\\
		  Server developed in \textbf{ASP.NET Web API}, Web App in \textbf{Knockout.js} and data stored in \textbf{SQL Server}.
		}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2014 -- 2017}
		{Engineer’s degree}
		{Warsaw University of Life Sciences}
		{
			Engineering of Computer Systems (Specialisation in \textbf{Networking} and \textbf{Security})\\
			Thesis: \it{Implementation of the service enabling two-step user verification}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Projects}

	\textbf{\href{https://github.com/matishadow/portkable-pass}{Portkable Pass}} - Password Manager without database, based on HMAC.\\
	\textbf{\href{https://github.com/matishadow/PicnicAuth}{PicnicAuth}} - Library for OTP generation.\\
	\textbf{\href{https://github.com/matishadow/NoRobots}{NoRobots}} - Web scraper for a banking website.
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Hobbies}

	\textbf{IT Security} - CTF competitions, finding vunerabilities.\\
	\textbf{Tech News} - Researching new frameworks, languages, programming concepts. 
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{Polish} - native\\
	\textbf{English} - fluent\\
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
